The human in the loop: volunteer computing as a socio-technical system

### 2016-02-28 Alife16/paper.tex
SoA
Few edits,

JavaScript can be used either for unwitting
\citep{unwitting-ec,boldrin2007distributed} or volunteer 
\citep{langdon:2005:metas,gecco07:workshop:dcor} distributed
evolutionary computation and it has been used ever since by several
authors, including more recent efforts
\citep{Desell:2008:AHG:1389095.1389273,duda2013distributed,DBLP:journals/corr/abs-0801-1210}. Many other researchers have
used Java \citep{chong:1999:jDGPi} and others have gone away from the
server-based paradigm to embrace peer to peer systems
\citep{jin2006constructing,10.1109/ICICSE.2008.99,DBLP:conf/3pgcic/GuervosMFEL12}. These computing
platforms avoid single points of failure (the server) but, since they
need a certain amount of infrastructure installed to start, the
threshold to join them is much lower.

On the other hand, we are also interested in measuring the performance
of volunteer computing systems, an area in which there have been
relatively few efforts.
There were some initial attempts to avoid the differences in performance
that could be obtained from volunteers  by making
the algorithm adaptive to the kind of resources allotted to it
\citep{milani2004online}, which is actually not such a big problem in
algorithms such as the EA that can easily be
parallelized via population splitting or farming out evaluations to all
the nodes available. Lately, several approaches have focused on the
fault-tolerance of volunteer algorithms
\citep{gonzalez2010characterizing} which it can, of course, be studied in
the more general context of distributed computing 
\citep{nogueras2015studying} or including it in a more general study of the
performance of the EA itself
\citep{DBLP:journals/gpem/LaredoBGVAGF14}. This performance cannot be
measured without understanding the dynamics of this kind of systems. Initial
work was done for peer to peer systems by Stutzbach et
al. \citep{stutzbach2006understanding} and extended to volunteer
computing by Laredo et al. \citep{churn08,laredo2008rcp}. A similar
study was performed by Martínez et al. on the Capataz system
\citep{martinez2015capataz}; however in this case the number of
computers used was known in advance and the main focus was on
measuring speed up and how job bundling helped to reduce overhead and
enhance performance.

>>>>

JavaScript can be used for either unwitting
\citep{unwitting-ec,boldrin2007distributed} or volunteer 
\citep{langdon:2005:metas,gecco07:workshop:dcor} distributed
evolutionary computation and it has been used ever since by several
authors, including more recent efforts
\citep{Desell:2008:AHG:1389095.1389273,duda2013distributed,DBLP:journals/corr/abs-0801-1210}. Many other researchers have
used Java \citep{chong:1999:jDGPi} and others have gone away from the
server-based paradigm to embrace peer to peer systems
\citep{jin2006constructing,10.1109/ICICSE.2008.99,DBLP:conf/3pgcic/GuervosMFEL12}. These computing
platforms avoid single points of failure (the server) but, since they
need a certain amount of infrastructure installed to start, the
threshold to join them is much lower.

On the other hand, we are also interested in measuring the performance
of volunteer computing systems, an area in which there have been
relatively few efforts.
There were some initial attempts to avoid the differences in performance
that could be obtained from volunteers  by making
the algorithm adaptive to the kind of resources allotted to it
\citep{milani2004online}, which is actually not such a big problem in
algorithms such as the EA that can be easily 
parallelized via population splitting or by farming out the evaluation to all
the nodes available. Lately, several approaches have focused on the
fault-tolerance of volunteer algorithms %volunteer systems?
\citep{gonzalez2010characterizing} which it can, of course, be studied in
the more general context of distributed computing 
\citep{nogueras2015studying} or including it in a more general study of the
performance of the EA itself
\citep{DBLP:journals/gpem/LaredoBGVAGF14}. This performance cannot be
measured without first understanding the dynamics of this kind of systems. Initial
work was done for peer to peer systems by Stutzbach et
al. \citep{stutzbach2006understanding} and extended to volunteer
computing by Laredo et al. \citep{churn08,laredo2008rcp}. A similar
study was performed by Martínez et al. on the Capataz system
\citep{martinez2015capataz}; however in this case the number of
computers used was known in advance and the main focus was on
measuring the speed up and how job bundling helped to reduce overhead and
enhance performance.
